Papers

### 2025-12-23 quarto/index.qmd
update

---
about:
  id: az-heading
  template: trestles
  image: img/aston.jpg
  image-width: 160px
  image-shape: rounded
  links:
    - icon: bi-envelope
      href: img/email.png

@@

* **A. Zhang**, Z. C. Lipton, M. Li, and A. J. Smola<br>
 	<a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a><br>
	*Cambridge University Press*, 2023<br>
	* Adopted at 500 universities from 70 countries
	* <a href="https://raw.githubusercontent.com/d2l-ai/d2l-zh/master/static/frontpage/_images/sales/jd-2023020304-all-ai-zh-4.png" target="_blank">Best seller</a> in China 
	<br>
	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-en&type=star&count=true" frameborder="0" scrolling="0" width="120" height="30" title="GitHub"></iframe> <iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-zh&type=star&count=true" frameborder="0" scrolling="0" width="120" height="30" title="GitHub"></iframe>

>>>>

---
about:
  id: az-heading
  template: trestles
  image: img/aston.jpg
  image-width: 160px
  image-shape: rounded
  links:
    - icon: bi-envelope
      href: img/email.png
    - icon: twitter-x
      href: https://twitter.com/astonzhangAZ
    - icon: google
      href: https://scholar.google.com/citations?user=WXOaxKMAAAAJ
    - icon: linkedin
      href: https://www.linkedin.com/in/astonzhang/

@@

* **A. Zhang**, Z. C. Lipton, M. Li, and A. J. Smola<br>
 	<a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a><br>
	*Cambridge University Press*, 2023<br>
	* Adopted at 500 universities from 70 countries
	* <a href="https://raw.githubusercontent.com/d2l-ai/d2l-zh/master/static/frontpage/_images/sales/jd-2023020304-all-ai-zh-4.png" target="_blank">Best seller</a> in China 
	<br>
	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-en&type=star&count=true" frameborder="0" scrolling="0" width="120" height="25" title="GitHub"></iframe>
	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-zh&type=star&count=true" frameborder="0" scrolling="0" width="120" height="25" title="GitHub"></iframe>
